---
title: "Results"
author: "Shozen Dan"
format: html
editor: visual
---

```{r}
# Load libraries
library(readr)
library(purrr)
library(ggplot2)
library(ggsci)
library(dplyr)

# Aesthetics
ic_color_palette <- c("#00548F", "#7244E5", "#CC3DC7", "#CC3D5C", "#CC893D", "#A3CC3D", "#3DCC41", "#3DCCAD")
```

## Repeat Effect

```{r}
read_rho <- function(model_name){
  in_dir <- "~/Imperial/contact-survey-fatigue-outputs/results"
  df <- read_rds(file.path(in_dir, model_name, "post_rho.rds"))
  df$model <- model_name
  return(df)
}

models <- c("pois_longit_gp",
            "pois_longit_logistic")
df <- map_dfr(models, read_rho)
df_iid <- read_rho("pois_longit_iid")
df_iid$r <- df_iid$r + 1

# Plot the results of the iid model using geom_point() and geom_linerange()
ggplot(df, aes(r, `50%`)) +
  
  geom_ribbon(data = df %>% filter(model == "pois_longit_gp"),
              aes(ymin = `2.5%`, ymax = `97.5%`, fill = "GP"), alpha = 0.3) +
  geom_line(data = df %>% filter(model == "pois_longit_gp"), aes(color = "GP")) +
  geom_line(data = df %>% filter(model == "pois_longit_logistic"), aes(color = "Logistic")) +
  geom_ribbon(data = df %>% filter(model == "pois_longit_logistic"),
              aes(ymin = `2.5%`, ymax = `97.5%`, fill = "Logistic"), alpha = 0.3) +
  geom_linerange(data = df_iid, aes(ymin = `2.5%`, ymax = `97.5%`, color = "iid"), show.legend = F) +
  geom_point(data = df_iid, aes(r, `50%`, color = "iid"),
             fill = "white",
             size = 3,
             shape = 21) +
  scale_color_manual(values = ic_color_palette[c(1,6,4)], breaks = c("iid", "GP", "Logistic")) +
  scale_fill_manual(values = ic_color_palette[c(1,6,4)], breaks = c("iid", "GP", "Logistic")) +
  scale_x_continuous(breaks = seq(0, 10, 2)) +
  labs(x = "Number of repeated participation [r]", y = expression(rho(r))) +
  theme_bw() +
  guides(
    color = guide_legend(
      override.aes = list(shape = c(21,NA,NA),
                          linetype = c(0, 1, 1),
                          color = ic_color_palette[c(1,6,4)],
                          fill = c("white", NA, NA)),
      title = "Model"
    ),
    fill = "none"
  )

# ggsave("../../figures/repeat_effect.pdf", width = 15, height = 8, units = "cm")
```

The plot above shows the posterior means and 95% credible intervals of three different repeat effect models: *i.i.d.*, GP, and diminishing logistic function. The *i.i.d.* and GP models produced similar results where the effect of repeated participation steadily increase with each participation and shows signs of tapering off after the 9-th or 10-th repeat. The logistic model is a good approximation of the non-parametric alternatives and describes the effect of repeat with a smooth monotonically decreasing curve that saturates approximately at −1.5.

### Half Saturation Point

For the logistic function
$$
\rho(r \\ \alpha, \beta) = -\gamma\left(1 - \frac{\exp(\alpha)r^\beta}{1+\exp(\alpha)r^{\beta}}\right)
$$
the half saturation point is
$$
r = \exp\left( -\frac{\alpha}{\beta} \right)
$$

and the quantity
$$
1 - \frac{e\exp(\alpha)r^\beta}{1 + \exp(\alpha)r^\beta}
$$
can be interpreted as percent fatigue. By setting an appropriate cut-off (say 95%) we can make a decision on the number of repeats we model.

## Effect on average number of contacts

```{r}
covimod_data <- read_rds("~/Imperial/contact-survey-fatigue/data/COVIMOD/COVIMOD_data_2022-12-29.rds")
df_part <- covimod_data$part
df_survey_date <- df_part %>% 
  group_by(wave) %>%
  summarise(survey_date = first(date))

read_tau <- function(model_name){
  in_dir <- "~/Imperial/contact-survey-fatigue-outputs/results"
  df <- read_rds(file.path(in_dir, model_name, "post_tau.rds"))
  df$model <- model_name
  df$t <- seq(1, 10)
  return(df)
}

models <- c("pois_longit_iid",
            "pois_longit_gp",
            "pois_longit_logistic",
            "pois_longit_noadj")
df <- map_dfr(models, read_tau)

df <- df %>% 
  mutate(
    `2.5%` = ifelse(model != "pois_longit_logistic", NA, `2.5%`),
    `25%` = ifelse(model != "pois_longit_logistic", NA, `25%`),
    `75%` = ifelse(model != "pois_longit_logistic", NA, `75%`),
    `97.5%` = ifelse(model != "pois_longit_logistic", NA, `97.5%`)
  )

df$model <- factor(df$model, levels = c("pois_longit_noadj",
                                        "pois_longit_iid",
                                        "pois_longit_gp",
                                        "pois_longit_logistic"))

df <- df %>% 
  left_join(df_survey_date, by = join_by(t == wave))

ggplot(df, aes(survey_date, `50%`)) +
  geom_line(aes(color = model)) +
  labs(x = "Wave", y = expression(exp(alpha + tau(t))), color = "Model") +
  scale_x_date(expand = c(0, 0)) +
  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, 2)) +
  scale_color_manual(values = c("gray30", ic_color_palette[c(1,6,4)]),
                     labels = c("No adjustment", "iid", "GP", "Logistic")) +
  theme_bw() + 
  theme(
    legend.position = "bottom",
    legend.margin = margin(t = -0.2, unit = "cm"),
  )

# ggsave("../../figures/time-trends.png", width = 15, height = 8, units = "cm")
```
